\section{Mobile Interface}
Design is a crucial topic in developing a mobile application. A key issue when
conceiving a design is thinking that having a "nice-looking" app is enough to achieve it. The first error while approaching the design phase is not to put the user at the centre. When software is intuitive, users have a more pleasant experience and tend to use it again while, if they find difficulties, their painful experience will make them abandon the application.\newline

The first things to understand during the design phase was how users would have moved inside Expire App. We wanted to group the various elements in characterizing our offer by domain, to make as most intuitive as possible
for users to add for eg., a product, or view a recipe. To achieve our objective, we divided the application into five main sections:

\begin{itemize}
    \item \textbf{Recipe screen: } containing the list of recipes based on the products that the user has
    
    \item \textbf{Shopping List screen: } containing lists of products that the user can insert
    
    \item \textbf{Home screen: } containing the list of products that the user has, it gives also the possibility to add new products
    
    \item \textbf{Statistics screen: } containing some statistical infos about the products that the user has (for eg. the quantity of salt in products, quantity of fat, etc..)
    
    \item \textbf{User info screen: } containing profile informations, and gives to the user the possibility to change his/her display name, leave a family, join a family, and logout.
\end{itemize}

To let the user navigate among these sections, we used a Tab selector, which
provides some buttons on the bottom of the display, where each button corresponds to a single screen.\newline

\textbf{Interactive components: } One of the main goal in developing Expire App, is to create a user friendly interface, so our team decided to put particular focus on how interactive elements, like buttons and cards, should behave. To achieve this, as already stated Expire App is developed as well as for different platforms, but also for different screen resolutions and sizes, including landscape versions. Next sections will show the screens related to each of the views listed above.

\input{./Chapters/Chapter4/4.2.1AuthScreen.tex}
\input{./Chapters/Chapter4/4.2.2HomeScreen.tex}
\input{./Chapters/Chapter4/4.2.3RecipeScreen.tex}
\input{./Chapters/Chapter4/4.2.4ShoppingListScreen.tex}
\input{./Chapters/Chapter4/4.2.5StatisticsScreen.tex}
\input{./Chapters/Chapter4/4.2.6UserInfoScreen.tex}